### 2015-05-14 conclusion.tex
fix

In this paper we presented \whoop, a new fully automatic approach for detecting all possible data races in device drivers. Compared to traditional data race detection techniques that are based on happens-before and typically attempt to explore as many thread interleavings as possible (and thus face code coverage and scalability issues), \textsc{Whoop} uses over-approximation and symbolic pairwise lockset analysis, which has the potential to scale well. Exploiting the race-freedom guarantees provided by \whoop, we showed that we can achieve a sound partial-order reduction that can significantly accelerate \corral, a state-of-the-art concurrent bug-finder. Combining \whoop and \corral, we analyzed \sizeOfBenchmarks drivers from the 4.0 Linux kernel distribution, showing that our technique can analyze programs 1.5--20$\times$ faster than standalone \corral.

>>>>

In this paper we presented \whoop, a new fully automatic approach for detecting all possible data races in device drivers. Compared to traditional data race detection techniques that are based on happens-before and typically attempt to explore as many thread interleavings as possible (and thus face code coverage and scalability issues), \textsc{Whoop} uses over-approximation and symbolic pairwise lockset analysis, which has the potential to scale well. Exploiting the race-freedom guarantees provided by \whoop, we showed that we can achieve a sound partial-order reduction that can significantly accelerate \corral, a state-of-the-art concurrent bug-finder. Combining \whoop and \corral, we analyzed \sizeOfBenchmarks drivers from the 4.0 Linux kernel distribution, showing that our technique can analyze drivers 1.5--20$\times$ faster than standalone \corral.
